---
title: "Charité Open Access Dashboard"
output: 
  flexdashboard::flex_dashboard:
    theme:
      version: 4
      navbar-bg: "#e97202"
      base_font: "'Source Sans Pro', Calibri, Candara, Arial, sans-serif"
    orientation: rows
    navbar:
      - { title: "Charité Medical Library", href: "https://bibliothek.charite.de", align: right }
    vertical_layout: scroll
    css: styles.css

# author: Jan Taubitz
# email: jan.taubitz@charite.de
# source_code: https://github.com/medbib-charite/oa-dashboard
---

```{r setup, include=FALSE}
library(flexdashboard)
```

```{r}
source("data_1.R", encoding = 'UTF-8')
```

Dashboard {data-icon="fa-globe"}
===================================== 

Row {.no-title}
-----------------------------------------------------------------------

###
<font size="5">The Charité Medical Library presents data about open access publishing in journal articles at the Charité in interactive, clickable diagrams. This dashboard is complementary to the [Charité Metrics Dashboard](https://s-quest.bihealth.org/charite-dashboard/) from the BIH QUEST Center at Charité.</font>



Row 
-----------------------------------------------------------------------

```{r}
##+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
## Analysis for gauges
##+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

load("data/data_unpaywall.Rda")

summary_is_oa <- data %>%
  group_by(jahr, oa_status, is_oa) %>%
  summarise(count = n()) %>%
  group_by(jahr) %>%
  mutate(perc = round(count / sum(count) * 100, 1)) %>% 
  # eliminate rounding differences created by different groupings
  group_by(jahr, is_oa) %>%
  summarise(count = sum(count), perc = sum(perc))

data_unpaywall_is_doaj <- data_unpaywall %>% # FIXME: Prozentwert is_doaj weniger umständlich berechnen (Anzahl TRUE / Anzahl gesamt); caution: data_unpaywall only contains articles with DOI. Others are not included in the calculation
  filter(year == 2020)
is_doaj <- sort(table(data_unpaywall_is_doaj$journal_is_in_doaj), decreasing = TRUE)
is_doaj <- round(is_doaj[[2]]/sum(is_doaj)*100, 1)

data_is_corresponding <- data %>% # FIXME: Prozentwert is_doaj weniger umständlich berechnen (Anzahl TRUE / Anzahl gesamt)
  filter(jahr == 2020)
is_corresponding <- sort(table(data_is_corresponding$corresponding_author_cha), decreasing = TRUE)
is_corresponding <- round(is_corresponding[[2]]/sum(is_corresponding)*100, 1)
```


### 2018: Percentage of open access among all articles involving Charité authors 

```{r}
rate <- summary_is_oa %>% filter(jahr == 2018 & is_oa == TRUE) %>% pull(perc)
gauge(rate, min = 0, max = 100, symbol = ' %', gaugeSectors(colors = "#e97202"))
```

### 2019: Percentage of open access among all articles involving Charité authors 

```{r}
rate <- summary_is_oa %>% filter(jahr == 2019 & is_oa == TRUE) %>% pull(perc)
gauge(rate, min = 0, max = 100, symbol = ' %', gaugeSectors(colors = "#e97202"))
```

### 2020: Percentage of open access among all articles involving Charité authors 

```{r}
rate <- summary_is_oa %>% filter(jahr == 2020 & is_oa == TRUE) %>% pull(perc)
gauge(rate, min = 0, max = 100, symbol = ' %', gaugeSectors(colors = "#e97202"))
```

### 2021: Percentage of open access among all articles involving Charité authors 

```{r}
rate <- summary_is_oa %>% filter(jahr == 2021 & is_oa == TRUE) %>% pull(perc)
gauge(rate, min = 0, max = 100, symbol = ' %', gaugeSectors(colors = "#e97202"))
```


Row 
-----------------------------------------------------------------------

### 2020: Charité corresponding author articles among articles involving Charité authors

```{r}
rate <- is_corresponding
gauge(rate, min = 0, max = 100, symbol = ' %', gaugeSectors(colors = "#e97202"))
```
### 2020: Percentage of articles involving Charité authors appearing in a DOAJ-listed journal 

```{r}
rate <- is_doaj
gauge(rate, min = 0, max = 100, symbol = ' %', gaugeSectors(colors = "#F4C244"))
```

Row {data-height=auto}
-----------------------------------------------------------------------

### Analysis 1

<font size="5"> Open access status among articles involving Charité authors and among articles with a Charité corresponding author</font>

Row {data-height=auto}
-----------------------------------------------------------------------

### 2016 - 2021: Articles involving Charité authors by OA status (in %)

```{r}
status_percent
```

### 2016 - 2021: Articles with a Charité corresponding author by OA status (in %)

```{r}
status_corresponding_percent
```

Row {data-height=auto}
-----------------------------------------------------------------------

### 2016 - 2021: Articles involving Charité authors by OA status (absolute numbers)

```{r}
status_absolute_spline
```

### 2016 - 2021: Articles with a Charité corresponding author by OA status (absolute numbers)

```{r}
status_corresponding_absolute_spline
```


Row {data-height=auto}
-----------------------------------------------------------------------

### Analysis 2

<font size="5"> Publishers and journals among articles involving Charité authors, by open access status</font>

Row {data-height=auto}
-----------------------------------------------------------------------

### 2020: Articles by publisher in absolute numbers 

```{r}
publisher_2020_absolute
```

### 2020: Articles by journal in absolute numbers

```{r}
journal_absolute
```

Row {.tabset}
-----------------------------------------------------------------------

### 2018 - 2020: Centrally funded articles with a Charité corresponding author; costs at top 10 publishers

```{r}
publisher_costs
```

### ... and by year

```{r}
publisher_costs_year
```

Row {data-height=auto}
-----------------------------------------------------------------------

### Analysis 3

<font size="5"> Open licenses under which articles involving Charité authors were published</font>

Row 
-----------------------------------------------------------------------

### 2016 - 2020: Licenses for all articles involving Charité authors

```{r}
load("charts/chart_lizenzen.Rda")
chart_lizenzen
```

### only 2020: Licenses for all articles involving Charité authors

```{r}
load("charts/chart_lizenzen_year_2020.Rda")
chart_lizenzen_year_2020
```

Data tables
=====================================

Row 
-----------------------------------------------------------------------

### Articles involving Charité authors, by OA status and year
```{r}
library(kableExtra)

load("data/data_unpaywall.Rda")

data_sum %>%
  kbl(align = "llll",
      col.names = c("year",
                    "oa_status",
                    "count",
                    "percent")) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "250px",
  box_css = "border: 1px solid #ddd; padding: 5px; "
)
```

Row 
-----------------------------------------------------------------------

### Articles with a Charité corresponding author, by OA status and year
```{r}
data_corresponding_sum %>%
  kbl(align = "llll",
      col.names = c("year",
                    "oa_status",
                    "count",
                    "percent")) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "250px",
  box_css = "border: 1px solid #ddd; padding: 5px; "
)
```

Row 
-----------------------------------------------------------------------

### Articles involving Charité authors, by OA status and license
```{r}
load("data/data_license_oa_status_final_count_2.Rda")

data_license_oa_status_final_count_2 %>%
  kbl(align = "lll")%>%
  kable_styling() %>%
  scroll_box(width = "100", height = "250px",
  box_css = "border: 1px solid #ddd; padding: 5px; "
)
```


About
=====================================

```{r}
library(htmltools)
  includeMarkdown('about.md')
```



