---
title: "Charité Open Access Dashboard"
output: 
  flexdashboard::flex_dashboard:
    theme:
      version: 4
      navbar-bg: "#e97202"
      base_font: "'Source Sans Pro', Calibri, Candara, Arial, sans-serif"
    orientation: rows
    navbar:
      - { title: "Charité Medical Library", href: "https://bibliothek.charite.de", align: right }
    vertical_layout: scroll
    css: styles.css

# authors: Jan Taubitz, Elena Gandert
# source_code: https://github.com/medbib-charite/oa-dashboard
---

```{r setup, include=FALSE}
library(flexdashboard)
```

```{r}
source("data_1.R", encoding = 'UTF-8')
```

Dashboard {data-icon="fa-globe"}
===================================== 

Row {.no-title}
-----------------------------------------------------------------------

###
<font size="5">The [Charité Medical Library](https://bibliothek.charite.de/en/) presents data about open access publishing in journal articles at the Charité in interactive, clickable diagrams. This dashboard is complementary to the [Charité Metrics Dashboard](https://s-quest.bihealth.org/charite-dashboard/) from the BIH QUEST Center at Charité.</font>


Row {.no-title}
-----------------------------------------------------------------------

###
<font size="5">Percentage of open access among all articles involving Charité authors</font>


Row 
-----------------------------------------------------------------------

```{r}
##+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
## Analysis for gauges
##+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

summary_is_oa <- data %>%
  group_by(jahr, oa_status, is_oa) %>%
  summarise(count = n()) %>%
  group_by(jahr) %>%
  mutate(perc = round(count / sum(count) * 100, 1)) %>% 
  # eliminate rounding differences created by different groupings
  group_by(jahr, is_oa) %>%
  summarise(count = sum(count), perc = sum(perc))

## 2022
data_2022 <- data %>%
  filter(jahr == 2022)

is_corresponding_2022 <- sort(table(data_2022$corresponding_author_cha), decreasing = TRUE)
is_corresponding_2022 <- round(is_corresponding_2022[[2]]/sum(is_corresponding_2022)*100, 1)

is_doaj_2022 <- sort(table(data_2022$journal_is_in_doaj), decreasing = TRUE)
is_doaj_2022 <- round(is_doaj_2022[[2]]/sum(is_doaj_2022)*100, 1)
```

### <b>2019</b>
```{r}
rate <- summary_is_oa %>% filter(jahr == 2019 & is_oa == TRUE) %>% pull(perc)
gauge(rate, min = 0, max = 100, symbol = ' %', gaugeSectors(colors = "#e97202"))
```

### <b>2020</b>
```{r}
rate <- summary_is_oa %>% filter(jahr == 2020 & is_oa == TRUE) %>% pull(perc)
gauge(rate, min = 0, max = 100, symbol = ' %', gaugeSectors(colors = "#e97202"))
```

### <b>2021</b>
```{r}
rate <- summary_is_oa %>% filter(jahr == 2021 & is_oa == TRUE) %>% pull(perc)
gauge(rate, min = 0, max = 100, symbol = ' %', gaugeSectors(colors = "#e97202"))
```

### <b>2022</b>
```{r}
rate <- summary_is_oa %>% filter(jahr == 2022 & is_oa == TRUE) %>% pull(perc)
gauge(rate, min = 0, max = 100, symbol = ' %', gaugeSectors(colors = "#e97202"))
```

Row 
-----------------------------------------------------------------------

### 2022: Charité corresponding author articles among articles involving Charité authors
```{r}
rate <- is_corresponding_2022
gauge(rate, min = 0, max = 100, symbol = ' %', gaugeSectors(colors = "#e97202"))
```

### 2022: Percentage of articles involving Charité authors appearing in a DOAJ-listed journal
```{r}
rate <- is_doaj_2022
gauge(rate, min = 0, max = 100, symbol = ' %', gaugeSectors(colors = "#F4C244"))
```

<!-- ### 2020: Percentage of articles involving Charité authors appearing in a DOAJ-listed journal -->

<!-- ```{r} -->
<!-- rate <- is_doaj_2020 -->
<!-- gauge(rate, min = 0, max = 100, symbol = ' %', gaugeSectors(colors = "#F4C244")) -->
<!-- ``` -->

Row {.no-title}
-----------------------------------------------------------------------
###
<font size="5"> Open access status among articles involving Charité authors and among articles with a Charité corresponding author</font>

Row {data-height=auto}
-----------------------------------------------------------------------

### 2017 - 2022: Articles involving Charité authors by OA status (in %)
```{r}
status_percent
```

### 2017 - 2022: Articles with a Charité corresponding author by OA status (in %)
```{r}
status_corresponding_percent
```

Row {data-height=auto}
-----------------------------------------------------------------------

### 2017 - 2022: Articles involving Charité authors by OA status (absolute numbers)
```{r}
status_absolute_spline
```

### 2017 - 2022: Articles with a Charité corresponding author by OA status (absolute numbers)
```{r}
status_corresponding_absolute_spline
```


Row {.no-title}
-----------------------------------------------------------------------
###
<font size="5"> Publishers and journals among articles involving Charité authors, by open access status</font>


<!-- Row {data-height=auto} -->
<!-- ----------------------------------------------------------------------- -->

<!-- ### 2020: Articles by publisher in absolute numbers  -->
<!-- ```{r} -->
<!-- publisher_2020_absolute -->
<!-- ``` -->

<!-- ### 2020: Articles by journal in absolute numbers -->
<!-- ```{r} -->
<!-- journal_2020_absolute -->
<!-- ``` -->


Row {data-height=auto}
-----------------------------------------------------------------------

### 2022: Articles by publisher in absolute numbers
```{r}
publisher_2022_absolute
```

### 2022: Articles by journal in absolute numbers
```{r}
journal_2022_absolute
```

Row {.tabset}
-----------------------------------------------------------------------

### 2018 - 2022: Centrally funded articles (with a Charité corresponding author); top 10 publishers by Charité expenditures
```{r}
publisher_costs
```

### ... and Charité expenditures by year
```{r}
publisher_costs_year
```


Row {.no-title}
-----------------------------------------------------------------------

###
<font size="5"> Open licenses under which articles involving Charité authors were published</font>

Row
-----------------------------------------------------------------------

<!-- ### 2016 - 2021: Licenses for all articles involving Charité authors -->
<!-- ```{r} -->
<!-- load("charts/chart_lizenzen.Rda") -->
<!-- chart_lizenzen -->
<!-- ``` -->

### only 2017: Licenses for all articles involving Charité authors
```{r}
load("charts/chart_lizenzen_year_2017.Rda")
chart_lizenzen_year_2017
```

### only 2022: Licenses for all articles involving Charité authors
```{r}
load("charts/chart_lizenzen_year_2022.Rda")
chart_lizenzen_year_2022
```

Data tables
=====================================

Row 
-----------------------------------------------------------------------

### Articles involving Charité authors, by OA status and year
```{r}
library(kableExtra)

summary_data_2017_2022 %>%
  kbl(align = "llll",
      col.names = c("year",
                    "oa_status",
                    "count",
                    "percent")) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "250px",
  box_css = "border: 1px solid #ddd; padding: 5px; "
)
```

Row 
-----------------------------------------------------------------------

### Articles with a Charité corresponding author, by OA status and year
```{r}
summary_corresponding_2017_2022 %>%
  kbl(align = "llll",
      col.names = c("year",
                    "oa_status",
                    "count",
                    "percent")) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "250px",
  box_css = "border: 1px solid #ddd; padding: 5px; "
)
```

Row 
-----------------------------------------------------------------------

### Articles involving Charité authors, by OA status and license
```{r}
load("data/data_license_oa_status_final_count_2.Rda")

data_license_oa_status_final_count_2 %>%
  kbl(align = "lll")%>%
  kable_styling() %>%
  scroll_box(width = "100", height = "250px",
  box_css = "border: 1px solid #ddd; padding: 5px; "
)
```


About
=====================================

```{r}
library(htmltools)
  includeMarkdown('about.md')
```



